What does the crowd believe? A hierarchical approach to estimating subjective beliefs from empirical data

### 2016-01-31 text/01_CogSci_abstract/paper.tex
minor paper updates

\begin{abstract}
  Experimental participants' beliefs about everyday events are of theoretical interest on their
  own and also an important ingredient for model building---especially in Bayesian models of
  phenomena such as logical reasoning, future predictions, and language use. Here, we explore
  several recently used methods for measuring subjective beliefs about unidimensional
  contiguous properties, such as the likely price of a new watch. We use a hierarchical
  Bayesian model for inferring likely ``population-level beliefs'' as the central tendency of
  participants' individual-level beliefs.  Three different dependent measures are related to
  individual-level beliefs through likelihood ``linking functions:'' (i) judgements of
  (relative) likelihood of intervals of values via continuous sliders, (ii) a give-a-number
  task, and (iii) choice of the more likely of two intervals of values. Our results suggest
  that using averaged normalized slider ratings for binned quantities is a practical and fairly
  good approximator of inferred population-level beliefs.

@@

Another possibility is to empirically measure subjective beliefs by \emph{give-a-number}
tasks. The simplest version would be this: being told that John just bought a new watch,
subjects are asked for a single numerical estimate of its price. This task is easy to
comprehend and implement, but a single number does not provide much information about the
subjective belief that it is (arguably) a manifestation of. One solution is to infer which
parameterized distribution best explains the observed number choices, either at the individual
level \citep{Manski2004:Measuring-Expec} or on the population level
\citep{TauberSteyvers2013:Inferring-Subje}.

More sophisticated \emph{give-a-number} tasks give more information, but can be rather complex
and more difficult to implement. A prominent method in economics uses \emph{scoring rules}
\citep{Savage1971:Elicitation-of-,AndersenFountain2014:Estimating-Subj,SchlagTremewan2014:A-penny-for-you}. Roughly
put, scoring rules are schemes of rewarding participants' answers that make sure that responses
(by rational subjects) faithfully reflect a measure of interest: the actual subjective
probability of an event, the mean of a distribution, a credible interval etc. Scoring-rule
tasks require participants to become sufficiently familiar with the (usually probabilistic)
payoff scheme. Another insightful, but also complex approach is to use a cleverly designed
\emph{iterated learning paradigm} \citep{LewandowskyGriffiths2009:The-Wisdom-of-I}.

In sum, there is tradeoff between simplicity of paradigms and their informativity. Ideally, we
would like to have an experimental method for measuring subjective beliefs that (i) gives us
sufficient and reliable-enough information about subjective beliefs to derive testable
predictions from cognitive models that rely on such information, (ii) is easy to understand by
the participants, (iii) is easy to implement by researchers whose focus and expertise is not
belief-elicitation as such, and that (iv) does not rely on sophisticated methods of extracting
the relevant information from the observed data. Moreover, the ideal method would be (v)
flexible enough to allow inferred subjective belief distributions beyond standard parameterized
distributions and (vi) would provide us with a reasonable approximation of a ``population-level
belief,'' i.e., an estimate of the central tendency or average of subjective beliefs in a given
population. The latter allows to use one set of subjects for measuring prior beliefs and
another for whatever other task is of interest.

A simple technique that seems to fit this bill is the \emph{binned histograms} task that has
recently been used with apparent success
\citep{KaoWu2014:Nonliteral-Unde,SchollerFranke2015:Semantic-values}. \mf{someone please add
  references: where did you use binned sliders?} Participants adjust sliders in order to
express their (relative) subjective beliefs about how likely it is that the value of an
uncertain contiguous quantity lies in some interval of possible values (a bin). E.g.,
participants read that John bought a watch.  To report their beliefs about the watch's price,
they adjust sliders whose endpoints are labelled as ``extremely likely'' and ``extremely
unlikely.'' Each slider corresponds to one out of 15 bins that partition the range of plausible
values (established by a pre-test). E.g., for the price of a watch bins could be ``\$0-\$50'',
``\$50-\$100'', etc. up to ``\$700-\$750'' and ``more than \$750''. Each subject's slider
ratings are normalized within each item, and the results are averaged across subjects to obtain
an estimate of the population's average belief about each item. These averaged normalized
slider ratings per bin (henceforth: mean slider ratings) look intuitively plausible and give
good results if fed into cognitive models that predict behavior in language or reasoning tasks,
for instance.

Explanatory success notwithstanding, the question remains whether mean slider ratings measure
what we would like them to. Are these good approximations of a central tendency of subjects'
individual beliefs? Are these measures consistent with subjects' behavior in other tasks, such
as \emph{give-a-number}, as well? To address this issue we collected data in a within-subject
from three task types: (i) \emph{binned histograms}, (ii) \emph{give-a-number} and (iii)
\emph{paired comparisons}, i.e., a direct comparison of two bins from the \emph{binned
  histograms} task. Using a Bayesian hierarchical model, we used the data from all three
dependent measures to infer likely latent subjective beliefs, where each subjective belief is,
intuitively, a noisy perturbation of a population-level belief. We find that mean \emph{a
  posteriori} population-level beliefs are approximated well by mean slider ratings, suggesting
that the latter may indeed be a plausible, yet cheap measure of ``what the crowd beliefs.''
Moreover, the model is able to capture subjects' behavior in all three task types reasonably
well, suggesting that what mean sliders measure is what we think it is: a population-level
central tendency of latent subjective beliefs.

\section{Experiment}

@@

\paragraph{Participants} We recruited 20 self-reported native speakers of English over Mechanical Turk.

\paragraph{Procedure and materials}

@@

\begin{table*}
  \footnotesize
  \centering
  \begin{tabular}{l p{2.2cm} p{2.5cm} p{3.5cm} p{3cm} p{2.5cm}}
	\toprule
	Item & Bins (units, min, max, step) & Context sentence & GAN question & BH frame & PC frame \\
	\midrule
    coffee & degrees, $<$44, $>200$, 12& X has just fetched himself a cup of coffee from the office vending machine. & What do you think the temperature of his coffee is?  & His coffee was the following temperatures & The temperature of his coffee is N degrees.\\
	commute & minutes, 0, $>$98, 7 & X commuted to work yesterday. & How many minutes do you think she spent commuting yesterday? & She commuted for the following numbers of minutes yesterday & She spent N minutes commuting.\\
	joke & children, 0, 14, 1  & X told a joke to 14 kids. & How many of the kids do you think laughed? & the following number of kids laughed & N of the children laughed.\\

	laptop & dollars, 0, $>$7500, 500& X bought a laptop. & How much do you think it cost? & The laptop cost the following numbers of dollars & The laptop cost \$N.\\
    marbles & marbles, 0, 14, 1 & X threw 14 marbles into a pool. & How many of the marbles do you think sank? & The following number of marbles sank & N of the marbles sank.\\

	movies & minutes, 0, $>210$, 16& X just went to the movies to see a blockbuster. & How many minutes long do you think the movie was? & The movie was the following numbers of minutes long & The movie was N minutes long.\\

	TV & hours, 0, $>$43, 3& X watched TV last week. & How many hours do you think he spent watching TV last week? & He watched TV for the following numbers of hours last week & He spent N hours watching TV.\\

	watch & dollars, 0, $>$750, 50 & X bought a watch.& How much do you think it cost? & It cost the following numbers of dollars & The watch cost \$N.\\
    \bottomrule
  \end{tabular}
  \caption{Experimental items. \emph{X} was a randomly generated name (different on each trial). \emph{N} was one of the bins.}
  \label{tab:Items}
\end{table*}

@@

Results are shown in \figref{fig:Results}. \figref{fig:Results} shows mean slider ratings in
relation to frequencies of number choices in the \emph{give-a-number} task. It looks like the
latter could be samples from the former, with a tendency to modal choices. But, despite the use
of slider, some \emph{give-a-number} results still seem to reflect a tendency towards round or
salient numbers. E.g., in item \emph{coffee} more than 40\% of participants guessed that a
coffee from the vending machine was ca. 150 degrees Fahrenheit (bin 10). The results from the
\emph{paired comparison} seem consistent with the mean slider ratings as well, albeit not as
straightforwardly as one might think. This is clearest from the \emph{marbles} case. While the
mean slider ratings indicate that bins 2, 6 and 11 were all felt to be equally likely on
average, almost every participant chose the higher bin in direct bin comparisons 2 vs 6 and 6
vs 11. A potential explanation for this, which we will implement formally in the
data-generating model, is that the \emph{paired comparison} condition invited subjects to think
about what they thought was mostly likely the case (usually: bin 15 in the
\emph{marbles} case) and to choose the bin that is closest to that.

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \includegraphics[width = \textwidth]{plots/data_sliderNumber.pdf}
    \caption{Red: proportion of choosing a number in each bin on \emph{give-a-number} trials. Black: mean slider ratings on \emph{binned histogram} trials.}
    \label{fig:slider}
  \end{subfigure}

  \begin{subfigure}[b]{0.5\textwidth}
    \includegraphics[width = \textwidth]{plots/data_choice.pdf}
    \caption{Proportion of choosing the higher bin on \emph{paired comparison} trials.}
    \label{fig:lighting}
  \end{subfigure}

@@

To fill the structure in Figure~\ref{fig:ModelGraph} with life, we need to spell out three
parameterized link functions, one for each task type, and the relation between population-level
belief $Q_j$ to individual beliefs $P_{ij}$. Let's start with the latter. For fixed $Q_j$, the
idea is that $P_{ij}$ are noise-perturbed variants scattered around $Q_j$, with some parameter
$w$ to determine how much perturbation we should expect. To realize this, the model assumes
that $P_{ij}$ are distributed according to a Dirichlet distribution with weights given by
$w Q_{j}$:
\begin{align*}
  Q_j & \sim \text{Dirichlet}(1, \dots, 1) & w & \sim \text{Gamma}(2,0.1) \\
  P_{ij} & \sim \text{Dirichlet}( w Q_j)
\end{align*}
The higher $w$, the more likely it is that $P_{ij}$ is ``close'' to $Q_j$.

@@

Finally, consider the link function for bin comparisons. We are interested in the likelihood
with which participant $i$ selects the higher bin for item $j$ in bin comparison condition
$l$. Suppose $l$ is about comparing the lower bin $b_l$ to the higher $b_h$. The perhaps most
natural approach would be to link the likelihood of choosing $b_h$ over $b_l$ to the difference
between $P_{ijb_h}$ and $P_{ijb_l}$. However, as discussed above, This does not appear to be
what participants were doing. Indeed, a model that implements this idea failed to capture the
relevant regularities in the data blatantly. Another plausible link function is to assume that
what matters in bin comparisons is the distance to the mode of $P_{ij}$: soft-max prefer the
bin that is closer to the mode of $P_{ij}$; select randomly if both bins are equally far from
the prototype.\footnote{Notice that
  $(1 + \exp(2b(1-p^{\text{high}}_{ijl})) )^{-1} = \frac{\exp(b p^{\text{high}})}{\exp(b
    p^{\text{high}}) + \exp(b p^{\text{low}})}$
  with $p^\text{low}_{ijl} = 2 - p^\text{high}_{ijl}$.}
\begin{align*}
  c_{ijl} & \sim \text{Bern}( (1 + \exp(2b(1-p^{\text{high}}_{ijl})) )^{-1} ) \ \ \ 
  b  \sim \text{Gamma}(2,1) \\
  p^\text{high}_{ijl} & = \begin{cases}
    2 & \text{if $mode(P_{ij})$ is closer to higher} \\
    & \text{ bin of $l$ than to lower bin } \\ 1 & \text{if equal
      distance} \\ 0 & \text{otherwise}  
  \end{cases}
\end{align*}

@@

Means and bounds of 95\% HDIs of the posteriors for model parameters are in
Table~\ref{tab:SummaryStats}. Posterior credible levels of $w$ allow for a limited amount of
slack around $Q_j$. Values for $\kappa$ indicate that, on average, subjects may not have had a
preference for or against extreme slider ratings. Relatively high values of $a$ indicate that
subjects, on average, had a strong tendency to choose their mode in the \emph{give-a-number}
task.
\begin{table}[ht]
\centering
\begin{tabular}{rlllll}
 & $w$ & $\kappa$ & $\sigma$ & $a$ & $b$ \\ \hline
  lower & 14.65 &  0.98 &  0.26 & 22.04 &  1.11 \\ 
  mean & 15.55 &  0.99 &  0.28 & 27.43 &  1.27 \\ 
  upper & 16.48 &  0.99 &  0.31 & 32.95 &  1.42 \\ 
   \hline
\end{tabular}
\caption{Summary statistics for posterior on parameters}
\label{tab:SummaryStats}
\end{table}

Of most theoretical interest are posterior estimates of $Q_j$. Figure~\ref{fig:PosteriorQj}
shows means of the posterior $Q_j$, with their 95\% HDIs, alongside the averaged normalized
slider ratings. The latter provide a very good approximation of the latent, inferred
population-level beliefs. Inspection of posteriors of individual $P_{ij}$ shows that there is
ample variation between participants. Nonetheless, the way the model suggest we should think about
harnessing the individual $P_{ij}$s under a population-level central tendency is closely
approximated by simply averaging over slider ratings. Although the match is clearly not
perfect, it is good enough to maintain that the latter are a reasonable (enough) and practical
way of assessing what the crowd believes despite individual differences.

@@

Inferences based on the model are only as reliable as the model itself is plausible. Model
criticism is therefore important. Figure~\ref{fig:PPCs} shows posterior predictive checks at
the population-aggregate level for all of our three task types. For the binned histogram task,
posterior predictions are spot-on. Some of the give-a-number data is surprising even for
the model trained on this very data. This could have various reasons: (i) the give-a-number data does
not have a huge influence on the posterior likelihood, (ii) number choices may be influenced by
saliency and/or roundness of numbers after all. Finally, there is one condition in the paired
comparison task that the model definitely got wrong. This is the choice of what is more likely:
that one or that none of 14 marbles thrown into a pool would sink. The model would predict that
almost everybody should answer that it is more likely that one marble sank. But that is not
what we observe. It may be that participants revise beliefs about ``normality'' of the marbles,
while holding on to an assumption that all marbles behave in the same way 
\cite{DegenTessler2015:Wonky-worlds:-L}.

@@

\section{Conclusions}

There aspects of the data that the model does not capture well, but there are also natural
explanations for these discrepancies. It therefore does not seem implausible that subjects'
latent beliefs could have generated the data from all three task types roughly in the way that
the model assumes, with each subjective belief being an expression of a population-level
central tendency. If that is so, then mean slider ratings from the binned histogram task would
seem to be a practical and reliable approximation of what the crowd believes.

The data and model presented here suggest that mean slider ratings are consistent with other
measures of subjective belief, namely from give-a-number and paired comparison tasks. Future
research should evaluate whether this holds for other possible measures of subjective beliefs
as well, such as from inferring parameterized distributions, or the use of scoring rules or the
iterated learning paradigm.

It also remains to be checked if and how our results can be extended to other types of
uncertain variables. Here, we focused on uncertainty about unidimensional contiguous variables,
because that was what many previous Bayesian models needed for checking their predictions. It
remains to be seen whether the binned histogram task can be applied to higher-dimensional
variables. Also, although it is suggestive that our results extend to cases where uncertainty
about a binary event is measured with a single (similarly labelled slider), this should be
checked carefully.

>>>>

\begin{abstract}
  Experimental participants' beliefs about everyday events are both of theoretical interest in their own right and an important ingredient in model building---especially in cognitive Bayesian models of
  phenomena such as logical reasoning, future predictions, and language use. Here, we explore
  several recently used methods for measuring subjective beliefs about unidimensional
  contiguous properties, such as the likely price of a new watch. We use a hierarchical
  Bayesian model for inferring likely population-level beliefs as the central tendency of
  participants' individual-level beliefs.  Three different dependent measures are related to
  individual-level beliefs through likelihood linking functions: (i) judgements of
  (relative) likelihood of intervals of values via continuous sliders, (ii) a give-a-number
  task, and (iii) choice of the more likely of two intervals of values. Our results suggest
  that using averaged normalized slider ratings for binned quantities is a practical and fairly
  good approximator of inferred population-level beliefs.

@@

Another possibility is to empirically measure subjective beliefs by \emph{give-a-number}
tasks. The simplest version would be this: being told that John just bought a new watch,
participants are asked for a single numerical estimate of its price. This task is easy to
comprehend and implement, but a single number does not provide much information about the
subjective belief that it is a manifestation of. One solution is to infer which
parameterized distribution best explains the observed number choices, either at the individual
level \citep{Manski2004:Measuring-Expec} or on the population level
\citep{TauberSteyvers2013:Inferring-Subje}.

More sophisticated \emph{give-a-number} tasks give more information, but can be rather complex
and more difficult to implement. A prominent method in economics uses \emph{scoring rules}
\citep{Savage1971:Elicitation-of-,AndersenFountain2014:Estimating-Subj,SchlagTremewan2014:A-penny-for-you}. Roughly
put, scoring rules are schemes of rewarding participants' answers that make sure that responses
(by rational participants) faithfully reflect a measure of interest: the actual subjective
probability of an event, the mean of a distribution, a credible interval etc. Scoring-rule
tasks require participants to become sufficiently familiar with the (usually probabilistic)
payoff scheme. Another insightful, but also complex approach is to use a cleverly designed
\emph{iterated learning paradigm} \citep{LewandowskyGriffiths2009:The-Wisdom-of-I}.

\begin{table*}
  \footnotesize
  \centering
  \begin{tabular}{l p{2.2cm} p{2.5cm} p{3.5cm} p{3cm} p{2.5cm}}
	\toprule
	\textbf{Item} & \textbf{Bins (units, min, max, step)} & \textbf{Context sentence} & \textbf{GAN question} & \textbf{BH frame} & \textbf{PC frame} \\
	\midrule
    coffee & degrees, $<$44, $>200$, 12& X has just fetched himself a cup of coffee from the office vending machine. & What do you think the temperature of his coffee is?  & His coffee was the following temperatures & The temperature of his coffee is N degrees.\\
    	\midrule
	commute & minutes, 0, $>$98, 7 & X commuted to work yesterday. & How many minutes do you think she spent commuting yesterday? & She commuted for the following numbers of minutes yesterday & She spent N minutes commuting.\\
		\midrule
	joke & children, 0, 14, 1  & X told a joke to 14 kids. & How many of the kids do you think laughed? & the following number of kids laughed & N of the children laughed.\\
    	\midrule
	laptop & dollars, 0, $>$7500, 500& X bought a laptop. & How much do you think it cost? & The laptop cost the following numbers of dollars & The laptop cost \$N.\\
	\midrule
    marbles & marbles, 0, 14, 1 & X threw 14 marbles into a pool. & How many of the marbles do you think sank? & The following number of marbles sank & N of the marbles sank.\\
	\midrule
	movies & minutes, 0, $>210$, 16& X just went to the movies to see a blockbuster. & How many minutes long do you think the movie was? & The movie was the following numbers of minutes long & The movie was N minutes long.\\
	\midrule
	TV & hours, 0, $>$43, 3& X watched TV last week. & How many hours do you think he spent watching TV last week? & He watched TV for the following numbers of hours last week & He spent N hours watching TV.\\
	\midrule
	watch & dollars, 0, $>$750, 50 & X bought a watch.& How much do you think it cost? & It cost the following numbers of dollars & The watch cost \$N.\\
    \bottomrule
  \end{tabular}
  \caption{Experimental items. \emph{X} was a randomly generated name (different on each trial). \emph{N} was one of the bins.}
  \label{tab:Items}
\end{table*}

In sum, there is tradeoff between simplicity of paradigms and their informativity. Ideally, we
would like to have an experimental method for measuring subjective beliefs that (i) provides
sufficient and reliable-enough information about subjective beliefs to derive testable
predictions from cognitive models that rely on such information, (ii) is easy to understand by
 participants, (iii) is easy to implement by researchers whose focus and expertise is not
belief-elicitation as such, and that (iv) does not rely on sophisticated methods of extracting
the relevant information from the observed data. Moreover, the ideal method would be (v)
flexible enough to allow inferred subjective belief distributions beyond standard parameterized
distributions and (vi) would provide us with a reasonable approximation of a population-level
belief, i.e., an estimate of the central tendency or average of subjective beliefs in a given
population. The latter would warrant using one set of participants for measuring prior beliefs and
another for whatever other task is of interest.

A simple technique that seems to fit this bill is the \emph{binned histogram} task that has
recently been used with apparent success
\citep{KaoWu2014:Nonliteral-Unde,SchollerFranke2015:Semantic-values}. \mf{someone please add
  references: where did you use binned sliders?} Participants adjust sliders in order to
express their (relative) subjective beliefs about how likely it is that the value of an
uncertain contiguous quantity lies in some interval of possible values (a bin). E.g.,
participants read that John bought a watch.  To report their beliefs about the watch's price,
they adjust sliders whose endpoints are labelled as ``extremely likely'' and ``extremely
unlikely.'' Each slider corresponds to one out of 15 bins that partition the range of plausible
values (established by a pre-test). E.g., for the price of a watch bins could be ``\$0-\$50'',
``\$50-\$100'', etc. up to ``\$700-\$750'' and ``more than \$750''. Each participant's slider
ratings are normalized within each item, and the results are averaged across participants to obtain
an estimate of the population's average belief about each item. These averaged normalized
slider ratings per bin (henceforth: mean slider ratings) look intuitively plausible and yield
good results if fed into cognitive models that predict behavior in language or reasoning tasks,
for instance.

Explanatory success notwithstanding, the question remains whether mean slider ratings measure
what we would like them to. Are these good approximations of a central tendency of participants'
individual beliefs? Are these measures consistent with participants' behavior in other tasks, such
as \emph{give-a-number}, as well? To address this issue we collected data in a within-subject
from three task types: (i) \emph{binned histograms}, (ii) \emph{give-a-number} and (iii)
\emph{paired comparisons}, i.e., a direct comparison of two bins from the \emph{binned
  histograms} task. Using a Bayesian hierarchical model, we used the data from all three
dependent measures to infer likely latent subjective beliefs, where each subjective belief is,
intuitively, a noisy perturbation of a population-level belief. We find that mean \emph{a
  posteriori} population-level beliefs are approximated well by mean slider ratings, suggesting
that the latter may indeed be a plausible, yet cheap measure of what the crowd believes.
Moreover, the model is able to capture participants' behavior in all three task types reasonably
well, suggesting that what mean slider ratings measure is what we think it is: a population-level
central tendency of latent subjective beliefs.

\section{Experimental elicitation of prior beliefs}

@@

\paragraph{Participants, procedure and materials} We recruited 20 self-reported English native speakers  over Mechanical Turk.

@@

@@

\figref{fig:Results} shows mean slider ratings alongside the frequencies of number choices in the \emph{give-a-number} task. It looks like the
latter could be samples from the former, with a tendency to modal choices. But, despite the use
of sliders, some \emph{give-a-number} results still seem to reflect a tendency towards round or
salient numbers. E.g., in item \emph{coffee} more than 40\% of participants guessed that a
coffee from the vending machine was ca. 150 degrees Fahrenheit (bin 10). The results from the
\emph{paired comparison} seem consistent with the mean slider ratings as well, albeit not as
straightforwardly as one might think. This is clearest from the \emph{marbles} case. While the
mean slider ratings indicate that bins 2, 6 and 11 were all felt to be equally likely on
average, almost every participant chose the higher bin in direct bin comparisons 2 vs 6 and 6
vs 11. A potential explanation for this, which we will implement formally in the
data-generating model, is that the \emph{paired comparison} condition invited participants to think
about what they thought was mostly likely the case (usually: bin 15 in the
\emph{marbles} case) and to choose the bin that is closest to that.

\begin{figure}[t!]
  \centering
  \begin{subfigure}{0.5\textwidth}
    \includegraphics[width = \textwidth]{plots/data_sliderNumber.pdf}
    \caption{Red: proportion of choosing a number in each bin on \emph{give-a-number} trials. Black: mean slider ratings on \emph{binned histogram} trials.}
    \label{fig:slider}
  \end{subfigure}

  \begin{subfigure}{0.5\textwidth}
    \includegraphics[width = \textwidth]{plots/data_choice.pdf}
    \caption{Proportion of choosing the higher bin on \emph{paired comparison} trials.}
    \label{fig:lighting}
  \end{subfigure}

@@

To fill the structure in \figref{fig:ModelGraph} with life, we need to spell out three
parameterized link functions, one for each task type, and the relation between population-level
belief $Q_j$ to individual beliefs $P_{ij}$. Let's start with the latter. For fixed $Q_j$, the
idea is that $P_{ij}$ are noise-perturbed variants scattered around $Q_j$, with some parameter
$w$ to determine how much perturbation we should expect. To realize this, the model assumes
that $P_{ij}$ are distributed according to a Dirichlet distribution with weights given by
$w Q_{j}$:
\begin{align*}
  Q_j & \sim \text{Dirichlet}(1, \dots, 1) & w & \sim \text{Gamma}(2,0.1) \\
  P_{ij} & \sim \text{Dirichlet}( w Q_j)
\end{align*}
The higher $w$, the more likely it is that $P_{ij}$ is ``close'' to $Q_j$.

@@

Finally, consider the link function for bin comparisons. We are interested in the likelihood
with which participant $i$ selects the higher bin for item $j$ in bin comparison condition
$l$. Suppose $l$ is about comparing the lower bin $b_l$ to the higher $b_h$. The perhaps most
natural approach would be to link the likelihood of choosing $b_h$ over $b_l$ to the difference
between $P_{ijb_h}$ and $P_{ijb_l}$. However, as discussed above, this does not appear to be
what participants were doing. Indeed, a model that implements this idea failed to capture the
relevant regularities in the data blatantly. Another plausible link function is to assume that
what matters in bin comparisons is the distance to the mode of $P_{ij}$: soft-max prefer the
bin that is closer to the mode of $P_{ij}$; select randomly if both bins are equally far from
the prototype.\footnote{Notice that
  $(1 + \exp(2b(1-p^{\text{high}}_{ijl})) )^{-1} = \frac{\exp(b p^{\text{high}})}{\exp(b
    p^{\text{high}}) + \exp(b p^{\text{low}})}$
  with $p^\text{low}_{ijl} = 2 - p^\text{high}_{ijl}$.}
\begin{align*}
  c_{ijl} & \sim \text{Bern}( (1 + \exp(2b(1-p^{\text{high}}_{ijl})) )^{-1} ) \ \ \ 
  b  \sim \text{Gamma}(2,1) \\
  p^\text{high}_{ijl} & = \begin{cases}
    2 & \text{if $mode(P_{ij})$ is closer to higher} \\
    & \text{ bin of $l$ than to lower bin } \\ 1 & \text{if equal
      distance} \\ 0 & \text{otherwise}  
  \end{cases}
\end{align*}

@@

Means and bounds of 95\% HDIs of the posteriors for model parameters are in
Table~\ref{tab:SummaryStats}. Posterior credible levels of $w$ allow for a limited amount of
slack around $Q_j$. Values for $\kappa$ indicate that, on average, participants may not have had a
preference for or against extreme slider ratings. Relatively high values of $a$ indicate that
participants, on average, had a strong tendency to choose their mode in the \emph{give-a-number}
task.
\begin{table}[ht]
\centering
\begin{tabular}{rlllll}
 & $w$ & $\kappa$ & $\sigma$ & $a$ & $b$ \\ \hline
  lower & 14.65 &  0.98 &  0.26 & 22.04 &  1.11 \\ 
  mean & 15.55 &  0.99 &  0.28 & 27.43 &  1.27 \\ 
  upper & 16.48 &  0.99 &  0.31 & 32.95 &  1.42 \\ 
   \hline
\end{tabular}
\caption{Summary statistics for posterior on parameters}
\label{tab:SummaryStats}
\end{table}

Of most theoretical interest are posterior estimates of $Q_j$. \figref{fig:PosteriorQj}
shows means of the posterior $Q_j$, with their 95\% HDIs, alongside the averaged normalized
slider ratings. The latter provide a very good approximation of the latent, inferred
population-level beliefs. Inspection of posteriors of individual $P_{ij}$ shows that there is
ample variation between participants. Nonetheless, the way the model suggest we should think about
harnessing the individual $P_{ij}$s under a population-level central tendency is closely
approximated by simply averaging over slider ratings. Although the match is clearly not
perfect, it is good enough to maintain that the latter are a reasonable (enough) and practical
way of assessing what the crowd believes despite individual differences.

@@

Inferences based on the model are only as reliable as the model itself is plausible. Model
criticism is therefore important. \figref{fig:PPCs} shows posterior predictive checks at
the population-aggregate level for all of our three task types. For the binned histogram task,
posterior predictions are spot-on. Some of the give-a-number data is surprising even for
the model trained on this very data. This could have various reasons: (i) the give-a-number data does
not have a huge influence on the posterior likelihood, (ii) number choices may be influenced by
saliency and/or roundness of numbers after all. Finally, there is one condition in the paired
comparison task that the model definitely got wrong. This is the choice of what is more likely:
that one or that none of 14 marbles thrown into a pool would sink. The model would predict that
almost everybody should answer that it is more likely that one marble sank. But that is not
what we observe. It may be that participants revise beliefs about ``normality'' of the marbles,
while holding on to an assumption that all marbles behave in the same way 
\cite{DegenTessler2015:Wonky-worlds:-L}.

@@

\section{Conclusion}

The data and model presented here suggest that mean slider ratings are consistent with other
measures of subjective belief, namely from give-a-number and paired comparison tasks. Future
research should evaluate whether this holds for other possible measures of subjective beliefs
as well, such as from inferring parameterized distributions, the use of scoring rules, or the
iterated learning paradigm.

There are aspects of the data that the model does not capture well, but there are also natural
explanations for these discrepancies. It therefore does not seem implausible that participants'
latent beliefs could have generated the data from all three task types roughly in the way assumed by the model, with each subjective belief being an expression of a population-level
central tendency. If that is so, then mean slider ratings from the binned histogram task are a practical and reliable approximation of what the crowd believes.

Future research should investigate whether and how our results can be extended to other types of
uncertain variables. Here, guided by the needs of many previous Bayesian cognitive models, we focused on uncertainty about unidimensional contiguous variables. It
remains to be seen whether the binned histogram task can be applied to higher-dimensional
variables \jd{like what?}. Also, although it is suggestive that our results extend to cases where uncertainty
about a binary event is measured with a single (similarly labelled slider), this should be
checked carefully. \jd{what does this mean?}
